noam_final_analyses

### 2024-09-05 noam_final_analyses.Rmd
Added turnover models for site level

@@

emtrends(shannon_cv_site, pairwise ~ habitat, var = "algae_shannon_mean") # no significant differences
shannon_cv_emm_site <- emmip(shannon_cv_site,
                        habitat ~ algae_shannon_mean,
                        at = list(algae_shannon_mean = seq(0,10,0.1)), plotit = F, CIs = T)

@@

(synchrony_richness_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site,
             aes(x = algae_richness_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_richness_effects_site, aes(x = algae_richness_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_richness_effects_site, aes(x = algae_richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

(synchrony_shannon_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site,
             aes(x = algae_shannon_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_shannon_effects_site, aes(x = algae_shannon_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_shannon_effects_site, aes(x = algae_shannon_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

emtrends(synchrony_cv_site_macro, pairwise ~ habitat, var = "loreau_synchrony") # backreef different from outer17
synchrony_cv_emm_site_macro <- emmip(synchrony_cv_site_macro,
                        habitat ~ loreau_synchrony,
                        at = list(loreau_synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

@@

(synchrony_richness_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site_macro,
             aes(x = algae_richness_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_richness_effects_site_macro, aes(x = algae_richness_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_richness_effects_site_macro, aes(x = algae_richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

synchrony_shannon_site_macro <- glmmTMB(loreau_synchrony  ~ algae_shannon_mean*habitat, family = beta_family(link = "logit"),
                          data = diversity_stability_site_macro)
summary(synchrony_shannon_site_macro)
hist(residuals(synchrony_shannon_site_macro)) # a little chunky
plot(residuals(synchrony_shannon_site_macro) ~ fitted(synchrony_shannon_site_macro)) # slightly heteroskedastic
Anova(synchrony_shannon_site_macro)
# 
#                              Chisq Df Pr(>Chisq)   
# algae_richness_mean         0.2299  1    0.63161  
# habitat                     5.4261  3    0.14312  
# algae_richness_mean:habitat 9.1650  3    0.02718 *

@@

(synchrony_shannon_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site_macro,
             aes(x = algae_shannon_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_shannon_effects_site_macro, aes(x = algae_shannon_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_shannon_effects_site_macro, aes(x = algae_shannon_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

>>>>

inv_logit <- function(x){
  exp(x)/(1+exp(x))
}

sv_trans <- function(prop, s = 0.000005){
  (prop*(length(prop) - 1) + s)/length(prop)
  # where prop is the vector of the proportional value you're transforming, 
  # N is the sample size, which is specified by taking the number of rows/observations from a given dataframe,
  # and s is a small offset 
}

@@

emtrends(shannon_cv_site, pairwise ~ habitat, var = "algae_shannon_mean") # no significant differences
shannon_cv_emm_site <- emmip(shannon_cv_site,
                        habitat ~ algae_shannon_mean,
                        at = list(algae_shannon_mean = seq(0,10,0.01)), plotit = F, CIs = T)

@@

(synchrony_richness_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site,
             aes(x = algae_richness_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_richness_effects_site, aes(x = algae_richness_mean, y = inv_logit(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_richness_effects_site, aes(x = algae_richness_mean, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

(synchrony_shannon_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site,
             aes(x = algae_shannon_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_shannon_effects_site, aes(x = algae_shannon_mean, y = inv_logit(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_shannon_effects_site, aes(x = algae_shannon_mean, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

emtrends(synchrony_cv_site_macro, pairwise ~ habitat, var = "loreau_synchrony") # backreef and fringe different from outer17
synchrony_cv_emm_site_macro <- emmip(synchrony_cv_site_macro,
                        habitat ~ loreau_synchrony,
                        at = list(loreau_synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

@@

(synchrony_richness_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site_macro,
             aes(x = algae_richness_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_richness_effects_site_macro, aes(x = algae_richness_mean, y = inv_logit(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_richness_effects_site_macro, aes(x = algae_richness_mean, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

synchrony_shannon_site_macro <- glmmTMB(loreau_synchrony  ~ algae_shannon_mean*habitat, family = beta_family(link = "logit"),
                          data = diversity_stability_site_macro)
summary(synchrony_shannon_site_macro)
hist(residuals(synchrony_shannon_site_macro)) # a little chunky
plot(residuals(synchrony_shannon_site_macro) ~ fitted(synchrony_shannon_site_macro)) # slightly heteroskedastic
Anova(synchrony_shannon_site_macro)
# 
#                              Chisq Df Pr(>Chisq)   
# algae_shannon_mean         0.6238  1     0.4296
# habitat                    4.8196  3     0.1855
# algae_shannon_mean:habitat 2.2517  3     0.5218

@@

(synchrony_shannon_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site_macro,
             aes(x = algae_shannon_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_shannon_effects_site_macro, aes(x = algae_shannon_mean, y = inv_logit(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_shannon_effects_site_macro, aes(x = algae_shannon_mean, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

```{r site all turnover}
total_turnover_site<-
  turnover(
  df = site_long_data,
  time.var = "year",
  species.var = "taxa",
  abundance.var = "percent_cover",
  replicate.var = "site_habitat",
  metric = "total"
)
total_turnover_site$site_hab_year <- paste0(total_turnover_site$site_habitat, "_", total_turnover_site$year) # for merge
total_turnover_site <- merge(total_turnover_site, site_meta_df, by = c("year", "site_habitat", "site_hab_year") )

total_turnover_site$turnover_trans <- sv_trans(total_turnover_site$total)

total_turnover_mod_site <- glmmTMB(turnover_trans ~ year*habitat + (1 | site), family = beta_family(), data = total_turnover_site)
summary(total_turnover_mod_site)
hist(residuals(total_turnover_mod_site)) # a little stumpy nut not bad
plot(residuals(total_turnover_mod_site) ~ fitted(total_turnover_mod_site)) # negative trend
Anova(total_turnover_mod_site)
emtrends(total_turnover_mod_site, pairwise ~ habitat, var = "year") # differences between backreef and fringing
total_turnover_emm_site <- emmip(total_turnover_mod_site,
                        habitat ~ year,
                        at = list(year = seq(2008,2023,1)), plotit = F, CIs = T)

(turnover_site_plot <- 
  ggplot() +
  geom_point(data = total_turnover_site,
             aes(x = year, y = turnover_trans, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = total_turnover_emm_site, aes(x = year, y = inv_logit(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = total_turnover_emm_site, aes(x = year, ymin = inv_logit(LCL), ymax = inv_logit(UCL),
                                                  fill = habitat), alpha = 0.3) +
  geom_segment(aes(y = 1, yend = 1, x = 2006, xend = 2010), linewidth = 2, alpha = 1, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
    labs(x = "Year", y = "Total turnover\n") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) )

```
```{r site macro turnover}
total_turnover_site_macro<-
  turnover(
  df = site_long_macro,
  time.var = "year",
  species.var = "taxa",
  abundance.var = "percent_cover",
  replicate.var = "site_habitat",
  metric = "total"
)
total_turnover_site_macro$site_hab_year <- paste0(total_turnover_site_macro$site_habitat, "_", total_turnover_site_macro$year) # for merge
total_turnover_site_macro <- merge(total_turnover_site_macro, site_meta_df, by = c("year", "site_habitat", "site_hab_year") )

total_turnover_site_macro$turnover_trans <- sv_trans(total_turnover_site_macro$total)

total_turnover_mod_site_macro <- glmmTMB(turnover_trans ~ year*habitat + (1 | site), family = beta_family(), data = total_turnover_site_macro)
summary(total_turnover_mod_site_macro)
hist(residuals(total_turnover_mod_site_macro)) # slight negative skew
plot(residuals(total_turnover_mod_site_macro) ~ fitted(total_turnover_mod_site_macro)) # negative trend
Anova(total_turnover_mod_site_macro)
#               Chisq Df Pr(>Chisq)    
# year         73.936  1  < 2.2e-16 ***
# habitat      19.201  3  0.0002485 ***
# year:habitat 12.099  3  0.0070512 ** 
emtrends(total_turnover_mod_site_macro, pairwise ~ habitat, var = "year") # differences between forereef sites and fringing
total_turnover_emm_site_macro <- emmip(total_turnover_mod_site_macro,
                        habitat ~ year,
                        at = list(year = seq(2008,2023,1)), plotit = F, CIs = T)

(turnover_site_macro_plot <- 
  ggplot() +
  geom_point(data = total_turnover_site_macro,
             aes(x = year, y = turnover_trans, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = total_turnover_emm_site_macro, aes(x = year, y = inv_logit(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = total_turnover_emm_site_macro, aes(x = year, ymin = inv_logit(LCL), ymax = inv_logit(UCL),
                                                  fill = habitat), alpha = 0.3) +
  geom_segment(aes(y = 1, yend = 1, x = 2006, xend = 2010), linewidth = 2, alpha = 1, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
    labs(x = "Year", y = "Total turnover\n") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) )

```{r site all appearance}
appearance_site<-
  turnover(
  df = site_long_data,
  time.var = "year",
  species.var = "taxa",
  abundance.var = "percent_cover",
  replicate.var = "site_habitat",
  metric = "appearance"
)
appearance_site$site_hab_year <- paste0(appearance_site$site_habitat, "_", appearance_site$year) # for merge
appearance_site <- merge(appearance_site, site_meta_df, by = c("year", "site_habitat", "site_hab_year") )

appearance_site$turnover_trans <- sv_trans(appearance_site$appearance)

appearance_mod_site <- glmmTMB(turnover_trans ~ year*habitat , family = beta_family(), data = appearance_site)
# convergence issue from inclusion of random effect
summary(appearance_mod_site)
hist(residuals(appearance_mod_site)) # a little stumpy nut not bad
plot(residuals(appearance_mod_site) ~ fitted(appearance_mod_site)) # negative trend
Anova(appearance_mod_site)
#                Chisq Df Pr(>Chisq)    
# year         58.4417  1  2.094e-14 ***
# habitat       9.5344  3  0.0229685 *  
# year:habitat 18.4862  3  0.0003491 ***
emtrends(appearance_mod_site, pairwise ~ habitat, var = "year") # lagoons both diff from forereefs but not each other
appearance_emm_site <- emmip(appearance_mod_site,
                        habitat ~ year,
                        at = list(year = seq(2008,2023,1)), plotit = F, CIs = T)

(appearance_site_plot <- 
  ggplot() +
  geom_point(data = appearance_site,
             aes(x = year, y = turnover_trans, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = appearance_emm_site, aes(x = year, y = inv_logit(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = appearance_emm_site, aes(x = year, ymin = inv_logit(LCL), ymax = inv_logit(UCL),
                                                  fill = habitat), alpha = 0.3) +
  geom_segment(aes(y = 1, yend = 1, x = 2006, xend = 2010), linewidth = 2, alpha = 1, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
    labs(x = "Year", y = "Appearances\n") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) )

```
```{r site macro disappearance}
appearance_site_macro<-
  turnover(
  df = site_long_macro,
  time.var = "year",
  species.var = "taxa",
  abundance.var = "percent_cover",
  replicate.var = "site_habitat",
  metric = "appearance"
)
appearance_site_macro$site_hab_year <- paste0(appearance_site_macro$site_habitat, "_", appearance_site_macro$year) # for merge
appearance_site_macro <- merge(appearance_site_macro, site_meta_df, by = c("year", "site_habitat", "site_hab_year") )

appearance_site_macro$turnover_trans <- sv_trans(appearance_site_macro$appearance)

appearance_mod_site_macro <- glmmTMB(turnover_trans ~ year*habitat, family = beta_family(), data = appearance_site_macro) # same convergence issue
summary(appearance_mod_site_macro)
hist(residuals(appearance_mod_site_macro)) # stumpy
plot(residuals(appearance_mod_site_macro) ~ fitted(appearance_mod_site_macro)) # negative trend
Anova(appearance_mod_site_macro)
#               Chisq Df Pr(>Chisq)    
# year         45.8213  1  1.296e-11 ***
# habitat       5.8339  3   0.119979    
# year:habitat 13.7486  3   0.003268 ** 
emtrends(appearance_mod_site_macro, pairwise ~ habitat, var = "year") # fringing different from fore, backreef from outer10
appearance_emm_site_macro <- emmip(appearance_mod_site_macro,
                        habitat ~ year,
                        at = list(year = seq(2008,2023,1)), plotit = F, CIs = T)

(turnover_site_macro_plot <- 
  ggplot() +
  geom_point(data = appearance_site_macro,
             aes(x = year, y = turnover_trans, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = appearance_emm_site_macro, aes(x = year, y = inv_logit(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = appearance_emm_site_macro, aes(x = year, ymin = inv_logit(LCL), ymax = inv_logit(UCL),
                                                  fill = habitat), alpha = 0.3) +
  geom_segment(aes(y = 1, yend = 1, x = 2006, xend = 2010), linewidth = 2, alpha = 1, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
    labs(x = "Year", y = "Appearances\n") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) )

```{r site all disappearance}
disappearance_site<-
  turnover(
  df = site_long_data,
  time.var = "year",
  species.var = "taxa",
  abundance.var = "percent_cover",
  replicate.var = "site_habitat",
  metric = "disappearance"
)
disappearance_site$site_hab_year <- paste0(disappearance_site$site_habitat, "_", disappearance_site$year) # for merge
disappearance_site <- merge(disappearance_site, site_meta_df, by = c("year", "site_habitat", "site_hab_year") )

disappearance_site$turnover_trans <- sv_trans(disappearance_site$disappearance)

disappearance_mod_site <- glmmTMB(turnover_trans ~ year*habitat + (1|site), family = beta_family(), data = disappearance_site)
# no convergence issue
summary(disappearance_mod_site)
hist(residuals(disappearance_mod_site)) # positive skew
plot(residuals(disappearance_mod_site) ~ fitted(disappearance_mod_site)) # negative trend
Anova(disappearance_mod_site)
#                Chisq Df Pr(>Chisq)    
# year         10.402  1   0.001259 ** 
# habitat      22.685  3  4.698e-05 ***
# year:habitat 12.099  3   0.007053 ** 
emtrends(disappearance_mod_site, pairwise ~ habitat, var = "year") # backrreef different from outer 10
disappearance_emm_site <- emmip(disappearance_mod_site,
                        habitat ~ year,
                        at = list(year = seq(2008,2023,1)), plotit = F, CIs = T)

(disappearance_site_plot <- 
  ggplot() +
  geom_point(data = disappearance_site,
             aes(x = year, y = turnover_trans, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = disappearance_emm_site, aes(x = year, y = inv_logit(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = disappearance_emm_site, aes(x = year, ymin = inv_logit(LCL), ymax = inv_logit(UCL),
                                                  fill = habitat), alpha = 0.3) +
  geom_segment(aes(y = 1, yend = 1, x = 2006, xend = 2010), linewidth = 2, alpha = 1, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
    labs(x = "Year", y = "Disappearances\n") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) )

```
```{r site all turnover}
disappearance_site_macro<-
  turnover(
  df = site_long_macro,
  time.var = "year",
  species.var = "taxa",
  abundance.var = "percent_cover",
  replicate.var = "site_habitat",
  metric = "disappearance"
)
disappearance_site_macro$site_hab_year <- paste0(disappearance_site_macro$site_habitat, "_", disappearance_site_macro$year) # for merge
disappearance_site_macro <- merge(disappearance_site_macro, site_meta_df, by = c("year", "site_habitat", "site_hab_year") )

disappearance_site_macro$turnover_trans <- sv_trans(disappearance_site_macro$disappearance)

disappearance_mod_site_macro <- glmmTMB(turnover_trans ~ year*habitat + (1|site), family = beta_family(), data = disappearance_site_macro) # same here
summary(disappearance_mod_site_macro)
hist(residuals(disappearance_mod_site_macro)) # not bad
plot(residuals(disappearance_mod_site_macro) ~ fitted(disappearance_mod_site_macro)) # negative trend
Anova(disappearance_mod_site_macro)
#               Chisq Df Pr(>Chisq)    
#                Chisq Df Pr(>Chisq)    
# year         33.3709  1  7.616e-09 ***
# habitat      11.5079  3   0.009274 ** 
# year:habitat  1.5899  3   0.661677    
emtrends(disappearance_mod_site_macro, pairwise ~ habitat, var = "year") # no sig difference
disappearance_emm_site_macro <- emmip(disappearance_mod_site_macro,
                        habitat ~ year,
                        at = list(year = seq(2008,2023,1)), plotit = F, CIs = T)

(turnover_site_macro_plot <- 
  ggplot() +
  geom_point(data = disappearance_site_macro,
             aes(x = year, y = turnover_trans, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = disappearance_emm_site_macro, aes(x = year, y = inv_logit(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = disappearance_emm_site_macro, aes(x = year, ymin = inv_logit(LCL), ymax = inv_logit(UCL),
                                                  fill = habitat), alpha = 0.3) +
  geom_segment(aes(y = 1, yend = 1, x = 2006, xend = 2010), linewidth = 2, alpha = 1, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
    labs(x = "Year", y = "Disappearances\n") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) )
